Adopting agile in the large: motivations, success factors and challenges

### 2014-04-24 journal/article.tex
Internal issues

As stated by Research Question 1 we investigated the reasons organizations start
a transformation process towards agile software development. In most primary
reasons for starting the transformation were mentioned, and only 7 cases of 42
did not mention any reasons. In the cases giving no specific reason to change it
was simply mentioned that management had decided to change the organization.
The reasons for organizations to change that were found are presented in table
\ref{table:reasonstochange}.

@@

The internal issues relate to how software development is managed in the
organization. In many organizations the project management practice was in a
state of dysfunction, and it needed to be corrected. Management problems were
for instance constantly recurring crisis events [P30], managers ignoring
prioritization of tasks [P38], and reluctance towards focusing on delivering
business value [P49]. Some cases stated that projects simply failed [P21]. Some
organizations wanted to improve generic project management practice, such as
risk management [P8], management of offshoring [P38], and improving the quality
of life of team members [P44]. Several organizations were growing and
experienced that the old development method did not scale up [P16, P50, P51].
There was also a desire to improve team motivation and commitment, and
collaboration between management and developers [P39].

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

As stated by Research Question 1 we investigated the reasons organizations start
a transformation process towards agile software development. Most primary
studies mentioned reasons for starting the transformation, and only 7 cases of
42 did not mention any reasons. In the cases giving no specific reason to change
it was simply mentioned that management had decided to change the organization.
The identified reasons for organizations to change are presented in table
\ref{table:reasonstochange}.

@@

The internal issues relate to how software development is managed in the
organization. In many organizations the project management practice was in a
state of dysfunction, and it needed to be corrected. Management problems were
for instance constantly recurring crisis events [P30], managers ignoring
prioritization of tasks [P38], and reluctance towards focusing on delivering
business value [P49]. Some cases stated that projects simply failed [P21]. Some
organizations wanted to improve generic project management practice, such as
risk management [P8], management of offshoring [P38], and improving the quality
of life of team members [P44]. Several organizations were growing and
experienced that the old development method did not scale up [P16, P30, P50, P51].
There was also a desire to improve team motivation and commitment, and
collaboration between management and developers [P39].

@@

A slow process with long cycle times leading to late feedback was a problem in
the old model. A large investment was required before results were visible [P5],
and there was variances in expectations and what was delivered [P40]. A related
problem was late integration which caused extra work [P25]. As organizations
grew and products became more complex test cycles began to lengthen, which
hindered flexibility and reduced speed [P33, P50].

Yet another problem in managing development was problems with schedules.
Some cases described schedules as unpredictable and estimation being difficult
[P16, P30, P40, P51]. In other cases it was reported that release deadlines were
often missed [P19, P21, P33, P41].

Finally, the original process model was seen as a cause for quality problems.
Several studies mentioned a demand for better quality, and quality improvement
was set as a goal for the agile transformation [P25, P31, P41, P42]. Improvement
in external quality and customer satisfaction were also anticipated from agile
development [P2, P4]. Problems with technical debt were attributed to the
original process. Some cases reported on prioritizing new feature development
over bugfixes or fixing only the easiest issues [P30, P38].
